ODGI: understanding pangenome graphs

### 2022-02-11 manuscript/main.tex
row row row your boat, row your boat

\usepackage{orcidlink}

@@

The ODGI data structure (Algorithm~\ref{alg:structs}) allows algorithms that build and modify the graph to operate in parallel, without any global locks.
In \textit{odgi build}, we initially construct the node vector in a serial operation that scans across the input GFA file.
Then, we serially add edges in the $Node.edges$ vectors of pairs of nodes.
Finally, we create paths in serial, and extend them in parallel by obtaining the mutex $Node.lock$ for pairs of nodes and by adding the path step in their $Node.path\_steps$ vectors.
This parallelism speeds ODGI model construction by many-fold when testing against graphs made from assemblies produced by the HPRC (Figure~\ref{fig:build}).

@@

\input{fig_build_time}

@@

@@

>>>>

\usepackage{orcidlink}
\usepackage{paralist}

@@

The ODGI data structure (Algorithm~\ref{alg:structs}) allows algorithms that build and modify the graph to operate in parallel, without any global locks.
In \textit{odgi build}, we initially construct the node vector in a serial operation that scans across the input GFA file.
Then, we serially add edges in the $Node.edges$ vectors of pairs of nodes.
Finally, we create paths in serial, and extend them in parallel by obtaining the mutex $Node.lock$ for pairs of nodes and by adding the path step in their $Node.path\_steps$ vectors.
This parallelism speeds ODGI model construction by many-fold when testing against graphs made from assemblies produced by the HPRC (\autoref{Evaluation}).

@@

@@

\subsection{Evaluation}
\label{Evaluation}

We measured the efficiency of ODGI (VERSION!) and VG (VERSION) for routine pangenome tasks. In particular, we measured the execution time and memory usage 
\begin{inparaenum}[(i)]
	\item of transforming a GFAv1 into the tool's native format,
	\item the visualization of a pangenome graph, 
	\item the extraction of a subgraph, and
	\item the finding of path positions in a pangenome graph.
\end{inparaenum}
key graph operations, why
deNBI
data
threads (64haps), haps (16 threads)
general findings: VG sucks, hehehe

@@

\input{fig_evaluation}
